Accuracy and precision of zero-heat-flux temperature monitoring: a systematic review and meta- analysis

### 2019-09-21 zhf_manuscript/zhf_manuscript.Rmd
ggplot based prisma works good

```{r fig-1, fig.align="center", fig.cap="PRISMA Flow Diagram", echo=FALSE}
img <- magick::image_read("figure_one.png")
img %>% magick::image_scale("350")
```

>>>>

```{r fig-1, fig.align="center",fig.cap="PRISMA Flow Diagram", echo=FALSE}
prsm <- PRISMAstatement::flow_exclusions(
  incl_counts = c(129, 94, 23, 15),
  total_label = "References imported for screening",
  incl_labels = c("Studies screened", "Full-text assessed for eligibility", "Included"),
  excl_labels = c("Duplicates removed", "Excluded", "Full-text excluded"),
               width = 200, height = 200)
tiff("figure-one.tiff", width=7.5, height=7, units='in', res=300, compression = 'lzw')
prsm
PRISMAstatement:::prisma_pdf(prsm)
```
